quicR: An R Package for Real-Time Quaking Induced Conversion (RT-QuIC) Assays

### 2025-01-03 man/manuscript/manuscript.qmd
Updated manuscript.

---
title: "quicR: An R Package for Real-Time Quaking Induced Conversion (RT-QuIC) Assays"
author:
    - name: 
        given: Gage
        family: Rowden
      id: GR
      orcid: 0000-0002-7517-0480
      email: rowde002@umn.edu
      affiliation:
        name: University of Minnesota
        city: Saint Paul
        state: MN
      roles:
        Conceptualization
        Methodology
        Software
        Validation
        Formal analysis
        Investigation
        Resources
        Data curation
        Writing--original draft preparation
        Writing--review and editing
        Visualization
        Supervision
        Prject administration
      corresponding: true
abstract: Real-time quaking induced conversion (RT-QuIC) has quickly become an emerging diagnostic tool for protein misfolding disorders such as Creutzfeldt-Jakob disease and Parkinson's disease. Given that the technology is still relatively new, academic and industry standards have yet to be established. 'quicR' was developed to fill this lack of standardization by providing functions for both data curation and analysis.
keywords: quicR, R package, RT-QuIC, prion, CJD, Parkinson's
format: pdf
mainfont: Calibri
bibliography: references.bib
bibliographystyle: apa
---
```{r, echo=FALSE, message=FALSE}
library(quicR)
library(dplyr)
library(kableExtra)
library(readxl)
library(readr)

>>>>

---
title: "quicR: An R Package for Real-Time Quaking Induced Conversion (RT-QuIC) Assays"
author:
    - name: 
        given: Gage
        family: Rowden
      id: GR
      orcid: 0000-0002-7517-0480
      email: rowde002@umn.edu
      affiliation:
        name: University of Minnesota
        city: Saint Paul
        state: MN
      roles:
        Conceptualization
        Methodology
        Software
        Validation
        Formal analysis
        Investigation
        Resources
        Data curation
        Writing--original draft preparation
        Writing--review and editing
        Visualization
        Supervision
        Prject administration
      corresponding: true
abstract: Real-time quaking induced conversion (RT-QuIC) has quickly become an emerging diagnostic tool for protein misfolding disorders such as Creutzfeldt-Jakob disease and Parkinson's disease. Given that the technology is still relatively new, academic and industry standards have yet to be established. 'quicR' was developed to fill this lack of standardization by providing functions for both data curation and analysis.
keywords: quicR, R package, RT-QuIC, prion, CJD, Parkinson's
format: pdf
mainfont: Calibri
bibliography: references.bib
bibliographystyle: apa
---
```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(quicR)
library(dplyr)
library(kableExtra)
library(readxl)
library(readr)
